Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-27 appendix.tex
Fix paths for calling images in appendix

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only Phoenix data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.065 & 0.241 & & 38.955 & 0.000 & *** & 31.854 & 0.139
&\tabularnewline
NRLINE & 144.000 & 0.229 & & 174.000 & 0.000 & *** & 148.000 & 0.105
&\tabularnewline
maxL & 4.000 & 0.421 & & 5.000 & 0.087 & . & 4.000 & 0.452
&\tabularnewline
L & 2.188 & 0.544 & & 2.270 & 0.039 & * & 2.182 & 0.580 &\tabularnewline
ENTR & 0.513 & 0.526 & & 0.650 & 0.033 & * & 0.504 & 0.550
&\tabularnewline
rENTR & 0.467 & 0.290 & & 0.469 & 0.276 & & 0.459 & 0.310
&\tabularnewline
LAM & 32.051 & 0.284 & & 46.154 & 0.008 & ** & 30.769 & 0.314
&\tabularnewline
TT & 2.273 & 0.196 & & 2.400 & 0.072 & . & 2.400 & 0.063 &
.\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target Phoenix
data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.558 & 0.178 & & 37.377 & 0.000 & *** & 25.740 & 0.988
&\tabularnewline
NRLINE & 145.000 & 0.189 & & 169.000 & 0.000 & *** & 119.000 & 0.989
&\tabularnewline
maxL & 4.000 & 0.467 & & 5.000 & 0.084 & . & 4.000 & 0.454
&\tabularnewline
L & 2.207 & 0.368 & & 2.243 & 0.123 & & 2.193 & 0.509 &\tabularnewline
ENTR & 0.547 & 0.343 & & 0.610 & 0.104 & & 0.521 & 0.492
&\tabularnewline
rENTR & 0.498 & 0.135 & & 0.440 & 0.432 & & 0.474 & 0.244
&\tabularnewline
LAM & 38.462 & 0.073 & . & 48.718 & 0.000 & *** & 21.795 & 0.790
&\tabularnewline
TT & 2.500 & 0.017 & * & 2.235 & 0.280 & & 2.429 & 0.048 &
*\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
***\tabularnewline
NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
& ***\tabularnewline
maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
.\tabularnewline
L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
**\tabularnewline
ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
**\tabularnewline
rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
&\tabularnewline
LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
*\tabularnewline
TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
.\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
***\tabularnewline
NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
***\tabularnewline
maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
**\tabularnewline
L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
**\tabularnewline
ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
**\tabularnewline
rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
&\tabularnewline
LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
**\tabularnewline
TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
&\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
\end{figure}

\begin{figure}[!h]
\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
\end{figure}

>>>>

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only Phoenix data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.065 & 0.246 & & 38.955 & 0.000 & *** & 31.854 & 0.130
&\tabularnewline
NRLINE & 144.000 & 0.220 & & 174.000 & 0.000 & *** & 148.000 & 0.106
&\tabularnewline
maxL & 4.000 & 0.456 & & 5.000 & 0.082 & . & 4.000 & 0.461
&\tabularnewline
L & 2.188 & 0.555 & & 2.270 & 0.030 & * & 2.182 & 0.637 &\tabularnewline
ENTR & 0.513 & 0.527 & & 0.650 & 0.027 & * & 0.504 & 0.615
&\tabularnewline
rENTR & 0.467 & 0.273 & & 0.469 & 0.264 & & 0.459 & 0.344
&\tabularnewline
LAM & 32.051 & 0.290 & & 46.154 & 0.007 & ** & 30.769 & 0.333
&\tabularnewline
TT & 2.273 & 0.211 & & 2.400 & 0.071 & . & 2.400 & 0.073 &
.\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target Phoenix
data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.558 & 0.168 & & 37.377 & 0.000 & *** & 25.740 & 0.984
&\tabularnewline
NRLINE & 145.000 & 0.172 & & 169.000 & 0.000 & *** & 119.000 & 0.983
&\tabularnewline
maxL & 4.000 & 0.437 & & 5.000 & 0.088 & . & 4.000 & 0.440
&\tabularnewline
L & 2.207 & 0.355 & & 2.243 & 0.125 & & 2.193 & 0.500 &\tabularnewline
ENTR & 0.547 & 0.334 & & 0.610 & 0.100 & . & 0.521 & 0.494
&\tabularnewline
rENTR & 0.498 & 0.164 & & 0.440 & 0.411 & & 0.474 & 0.261
&\tabularnewline
LAM & 38.462 & 0.079 & . & 48.718 & 0.001 & *** & 21.795 & 0.798
&\tabularnewline
TT & 2.500 & 0.021 & * & 2.235 & 0.294 & & 2.429 & 0.042 &
*\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
***\tabularnewline
NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.001 & *** & 170.000 & 0.001
& ***\tabularnewline
maxL & 5.000 & 0.074 & . & 5.000 & 0.099 & . & 5.000 & 0.101
&\tabularnewline
L & 2.249 & 0.089 & . & 2.272 & 0.045 & * & 2.306 & 0.009 &
**\tabularnewline
ENTR & 0.619 & 0.080 & . & 0.653 & 0.040 & * & 0.705 & 0.007 &
**\tabularnewline
rENTR & 0.447 & 0.362 & & 0.471 & 0.246 & & 0.509 & 0.125
&\tabularnewline
LAM & 43.590 & 0.017 & * & 39.744 & 0.051 & . & 42.308 & 0.028 &
*\tabularnewline
TT & 2.267 & 0.222 & & 2.385 & 0.093 & . & 2.357 & 0.111
&\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 34.122 & 0.011 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
***\tabularnewline
NRLINE & 152.000 & 0.037 & * & 168.000 & 0.000 & *** & 173.000 & 0.000 &
***\tabularnewline
maxL & 5.000 & 0.090 & . & 5.000 & 0.081 & . & 7.000 & 0.005 &
**\tabularnewline
L & 2.276 & 0.026 & * & 2.280 & 0.024 & * & 2.312 & 0.002 &
**\tabularnewline
ENTR & 0.663 & 0.021 & * & 0.661 & 0.021 & * & 0.698 & 0.005 &
**\tabularnewline
rENTR & 0.478 & 0.236 & & 0.477 & 0.233 & & 0.434 & 0.459
&\tabularnewline
LAM & 34.615 & 0.186 & & 39.744 & 0.045 & * & 48.718 & 0.003 &
**\tabularnewline
TT & 2.250 & 0.236 & & 2.385 & 0.077 & . & 2.235 & 0.267
&\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
\end{figure}

@@

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
\end{figure}

@@

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
\end{figure}

@@

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
\end{figure}
